\documentclass[a4paper,10pt]{article}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}

% Define the format for section titles
\titleformat{\section}{\bfseries\Large}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries\large}{}{0em}{}

\begin{document}

\pagestyle{empty} % Avoid page number

% Personal Information
\begin{center}
    {\LARGE \textbf{Mario Diez Martínez}} 
    \vspace{0.2cm}
    Madrid, Spain | +34 699 564 964 | \href{mailto:10martinez.mario@gmail.com}{10martinez.mario@gmail.com} | \href{https://www.linkedin.com/in/mario-diez-martinez}{LinkedIn}
\end{center}

% Professional Summary
\section*{Professional Summary}
Results-driven Economist with experience in financial markets and project management. Proven ability to harness data analytics and quantitative methods to drive business efficiencies and innovate solutions. Adept at working in high-pressure environments and delivering insights for financial decision-making.

% Education Section
\section*{Education}
\textbf{Universidad Complutense de Madrid} \
\textbf{Bachelor of Economics, Specialization in Global Economics} \hfill Sep 2018 - Feb 2023
\begin{itemize}[left=0em]
    \item Relevant Subjects: Advanced Macroeconomics, Econometrics, Applied Econometrics.
    \item Thesis: ``Made in China 2025: a quantitative analysis''
\end{itemize}

% Professional Experience Section
\section*{Professional Experience}
\textbf{BBVA, Madrid, Spain} \
\textbf{Project Manager Intern} \hfill Jun 2022 - Dec 2022
\begin{itemize}[left=0em]
    \item Streamlined bank operation processes through the migration to a new reconciliations tool, enhancing efficiency.
    \item Led daily follow-ups with technical teams using agile methodologies, improving project coordination.
    \item Assisted in data cleaning using Excel and Python, ensuring data accuracy and integrity.
    \item Compiled and presented weekly project status reports to stakeholders using PowerPoint.
    \item Developed dashboards for reconciliation KPIs using Google BigQuery, Data Studio, and Looker.
\end{itemize}

\textbf{Arfima Trading SLU, Madrid, Spain} \
\textbf{Quantitative Trader and Researcher} \hfill Mar 2023 - May 2023
\begin{itemize}[left=0em]
    \item Traded futures in US fixed income, generating a monthly ROI of 4\%.
    \item Conducted fundamental analysis on fixed income spreads and oil, enhancing trading strategies.
    \item Utilized machine learning for data modeling, employing techniques such as Lasso and Ridge regressions.
    \item Visualized complex curve structures with Plotly, facilitating interactive data analysis.
    \item Participated in back office code maintenance, improving reporting and data extraction processes.
\end{itemize}

% Skills Section
\section*{Skills}
\textbf{Technical:} Python (Pandas, Scikit-learn, Scipy), SQL, VBA, Excel, Git, Data Visualization (Matplotlib, Plotly, Looker). \
\textbf{Financial \& Analytical:} Financial modeling, econometric analysis, machine learning, dashboard development, project management. \
\textbf{Languages:} English (Fluent), Spanish (Native).

% Projects Section
\section*{Projects}
\textbf{Auto-Video-Maker} \hfill 2023
\begin{itemize}[left=0em]
    \item Developed an app to automate short video creation for social media using Streamlit, OpenAI, and Eleven Labs.
    \item Implemented features for scripting, image, and audio integration. \href{https://github.com/elgask0/auto-video-maker}{GitHub}
\end{itemize}

% Publications Section
\section*{Publications}
\textbf{Diez Martínez, M.} (2023). Strategic Competition Through the China-Solomon Islands Security Pact. \textit{Revista Del Instituto Español De Estudios Estratégicos}, (20), pp. 69–102 / 307.

% Interests Section
\section*{Interests}
Geopolitics, global economics, chess, strategy video games, reading, artificial intelligence.

\end{document}